Reasoning About a Machine with Local Capabilities

### 2018-04-27 toplas/paper.tex
Added a word on modularity to the section on stack and return pointer management.

%\itoplassug{Suggestion: Make it more clear that this CC can be used to protect multiple components (reviewer A, ESOP), see tex comment.\\}
\begin{toplas}
  \textbf{Modularity} The calling convention ensures well-bracketed calls and local-state encapsulation for the caller, but not the callee. In the above presentation to make it easy to distinguish between the parties involved, we present the callee as some adversarial code that we do not trust. In reality, the callee could be well-behaved and wish to ensure well-bracketed calls and local-state encapsulation. The calling convention puts no restriction on the callee that the caller itself does not follow, so by following the calling convention, the callee would also get well-bracketedness and local-state encapsulation. Generally, the calling convention ensures the two properties for anyone that employ it, so it scales to the setting where multiple distrusting parties need to invoke each other and each of them can protect themself by using the calling convention.
\end{toplas}

>>>>

%\itoplassug{Suggestion: Make it more clear that this CC can be used to protect multiple components (reviewer A, ESOP), see tex comment.\\}
\begin{toplas}
  \textbf{Modularity} The calling convention ensures well-bracketed calls and
  local-state encapsulation for the caller, but not the callee. In the above
  presentation to make it easy to distinguish between the parties involved, we
  present the callee as some adversarial code that we do not trust. In reality,
  the callee could be well-behaved and wish to ensure well-bracketed calls and
  local-state encapsulation. The calling convention puts no restriction on the
  callee that the caller itself does not follow, so by following the calling
  convention, the callee would also get well-bracketedness and local-state
  encapsulation. Generally, the calling convention ensures the two properties
  for anyone who employs it, so it scales to the setting where multiple
  distrusting parties need to invoke each other and each of them can protect
  themself by using the calling convention.
\end{toplas}
